### 2021-07-29 doc/thesis/chapters/conclusion-and-prospect.tex
hls
comments
product design
re-structure the results

% NOTES:
%  - use Matlab Simulink HDL Coder and System Generator
%    as additional implementation variants
%
%
%
%
%
%

>>>>

% NOTES:
%
% Further steps:
%  - generate VHDL from Matlab receiver code
%  - use the common input file and feed it to GNU Radio;
%    also produce an output file with GNU Radio for comparison
%  - Develop HLS compiler independent code (optional)}
%    -- Different compilers use different #pragmas, etc.
%    -- These #pragmas need to be within the code, at the appropriate positions,
%       which makes it difficult to write compiler independent code....
%  - use Matlab Simulink HDL Coder and System Generator
%     as additional implementation variants
%  - use Intel oneAPI HLS compiler
%      -- try to develop compiler-independent code
%      -- how platform-independent is HLS?
%  - explore HLS optimizations
%  - explore HLS libraries (e.g. DSP library --> pre-made FIR filter)
%  - create another IP in the same system
%      -- due to the modular system design this is easy to do
%  - use Linux OS on the SoC, to enable live-data streaming with the RTL-SDR
%
%
%
%
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Advantages / Disadvantages}

easy and much faster to get complex HDL code, such as image/video processing, through libraries like OpenCV.\\
However, it may be less optimized.\\
A developer still needs to have a strong hardware background, to be able to understand what is being generated in hardware from x lines of code in HLS/Cpp.

### 2021-07-29 doc/thesis/chapters/results.tex
comments
data types
interfaces
code formatting
axi lite register engine
tb stuff
add audio output graphic
re-structure the results

%%%%%%%%%%%%%%%%%%%%
\chapter{Test Results}
\label{cha:Results}
  \section{Functionality}
  % Functionality same?
  % Sim speed of x min of recorded FM signal
  % lines of code
  \subsection{Implementation effort/time}
  \subsection{Hardware Utilization}
  \subsection{Others}

  % TODO Überlegungen in diesem Kapitel
  % kann Demodulator geändert werden? Bsp. von FM zu DAB+, QAM, etc..
  % - von matlab heraus VHDL generieren, etc

>>>>

%%%%%%%%%%%%%%%%%%%%
\chapter{Comparison and Results}
\label{cha:ComparisonAndResults}

This chapter presents the results that are achieved in the development of the FM Radio Receiver project, with the chosen different methods.
However, the main focus is to compare the results that are achieved with HLS and VHDL, since these are the major implementation variants of the project.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{General}

The main goal of this thesis is to implement an FM radio receiver in multiple different methods.
This includes GNU Radio, Matlab, VHDL and HLS.
The target functionality is to listen to the audio broadcast signal of an FM radio station.\\

All of these methods are implemented and the target functionality is achieved with all of them.
However, the level of detail that is required in the implementation, and the resulting effort and time it takes to implement the respective variant, differs by a large factor.\\

In the following sections, especially the HLS and VHDL implementations are compared on the basis of metrics, but also based on the experience during development.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Functionality}

Generally, both tools - HLS and VHDL - provide the capabilities to implement any functionality in one or the other method.
However,

% Functionality same?
% DSP yes, AXI no (FSM of axi-stream)
% unit tests

%%%%%%%%%%%%%%%%%%%%
\subsection{Audio Output}
% show plots of the common analyzer python script
Demodulated Signal

\includepicture [1.0] [0] {Comparison of the audio signal.} {audio_output_compare_all_ips} {img/matlab/audio_output_compare_all_ips}

%%%%%%%%%%%%%%%%%%%%
\subsection{Interfaces}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Code Development}

%%%%%%%%%%%%%%%%%%%%
\subsection{Lines of Code}
% of the entire project

%%%%%%%%%%%%%%%%%%%%
\subsection{Implementation Time}

% Implementation effort/time
%    -- see logged times; is subjective; had no previous knowledge
%    -- AXI interfaces --> huge effort in VHDL...
%        (mention Johannes Walter for generously providing/allowing the Register Engine script, adapted for this thesis)
%    -- drivers are auto-generated with HLS! huge time-saving..
%       (maybe show the code of AXI4-Lite interface and its generated driver
%        --> difference between R/W and RO!;
%        and show screenshots of the IP in the block design)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulation}
% Sim speed of x min of recorded FM signal

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Design}

% - The system level architecture that was chosen, can be applied to any DSP project. Simply replace the main IP, e.g. from FM to DAB+, QAM, etc. and the environment can run in the exact same way.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Deployment On Hardware}

%%%%%%%%%%%%%%%%%%%%
\subsection{Integration}
% IP generation and integration into Vivado

%%%%%%%%%%%%%%%%%%%%
\subsection{Hardware Utilization}
% --> utilization reports

%%%%%%%%%%%%%%%%%%%%
\subsection{Latency}
% --> utilization reports

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Applicability}
% of all implementation variants
%   GNU Radio for fast prototyping,
%   Matlab for research
%   HLS/VHDL for deployment on HW, product development
